Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-07-26 tex/test-WW-type-00z.tex
alexei
final

\preprint{\red{version ``01a''}; \today; JLAB-THY-18-XXXX}

@@

After first exploratory investigations of TMDs on the lattice
\cite{Hagler:2009mb,Musch:2010ka}, recent years have witnessed considerable
progress and improvements with regard to rigor, realism and methodology
\cite{Yoon:2017qzo, %PhysRevD.96.094508
Engelhardt:2015xja,%Phys.Rev. D93 (2016) no.5, 054501, 
Ji:2014hxa,%Phys.Rev. D91 (2015) 074009, 
Musch:2011er%Phys.Rev. D85 (2012) 094510
}.
However, numerical results from recent calculations are only available 
for a subset of observables, and the quantities calculated are not in a 
form that lends itself to straightforward tests of the WW-type relations 
as presented in this paper. Details about recent works and future 
perspectives are discussed at the end of this section.

@@

The leading--twist 6 TMDs 
$f_1^a, \; f_{1T}^{\perp a}, \; g_1^a, \; h_1^a, \;h_1^{\perp a},\; h_{1T}^{\perp a}$
and 2 FFs $D_1^a, \; H_1^{\perp a}$ provide a basis
in the sense that in WW-type approximation all other TMDs and FFs 
can either be expressed in terms of these basis functions or vanish.
Below we shall see that, under the assumption of the validity of WW-type 
approximations, it is possible to express all SIDIS structure functions
in terms of the basis functions. \AP{Notice that SIDIS alone is of course not sufficient to determine
   the basis functions uniquely because the 8 basis functions appear
   in 6 SIDIS leading-twist structure functions. It is crucial to take advantage of
   other processes (such as Drell-Yan and hadron production in
   $e^+e^-$ annihilation, which are indispensable for the determination
   of $f_1^a$ and $D_1^a$).}
%\AP{Notice that SIDIS alone is of course not sufficient to determine the basis
%functions uniquely: the 8 basis functions appear in 6 \AP{leading-twist} SIDIS structure functions.
%It is crucial to take advantage of other processes: Drell--Yan for PDFs and TMDs
%and hadron production in $e^+e^-$ annihilation for FFs. Other processes 
%play also important roles.}
%Notice that SIDIS alone is of course not sufficient to determine the basis
%functions uniquely: \AP{8 twist-2 TMDs (or 6 ``basis'' TMDs) and 2 twist-2 TMD FFs appear in 15 structure functions (8 twist-2 and 5 sub-leading). 
%Definitely hadron production in $e^+e^-$ annihilation data is needed, each FF couples with 4 different twist-2 TMD PDFs, and so for each FF we have a case with 5 unknowns accessible in 4 twist-2 observables.
%It is crucial to take advantage of  Drell--Yan process for TMDs
%and other processes 
%play also important roles.}

These basis functions allow us to describe, in WW-type approximation,
all other TMDs. The experiment will tell us how well the approximations work.
In some cases, however, we know in advance that the WW-type approximations 
have limitations, see next Section.

>>>>

\preprint{\red{version ``01a''}; \today; JLAB-THY-18-2775}

@@

After first exploratory investigations of TMDs on the lattice
\cite{Hagler:2009mb,Musch:2010ka}, recent years have witnessed considerable
progress and improvements with regard to rigor, realism and methodology
\cite{Yoon:2017qzo, %PhysRevD.96.094508
Engelhardt:2015xja,%Phys.Rev. D93 (2016) no.5, 054501, 
Ji:2014hxa,%Phys.Rev. D91 (2015) 074009, 
Musch:2011er%Phys.Rev. D85 (2012) 094510
}.
However, numerical results from recent calculations are only available 
for a subset of observables, and the quantities calculated are not in a 
form that lends itself to straightforward tests of the WW-type relations 
as presented in this paper. \AP{This assumption holds if renormalization is multiplicative and
   flavor-independent for the non-local lattice operators. This is
   not true for all lattice actions [64]. But presumably it is true
   if the lattice action preserves chiral symmetry, as it does in
   the present case. For the latest developments we refer the
   interested reader to Refs.~\cite{Alexandrou:2017dzj,Ishikawa:2017faj,Ji:2017oey,Yoon:2017qzo,Green:2017xeu,Zhang:2017bzy}.}

@@

The 6 leading--twist TMDs 
$f_1^a, \; f_{1T}^{\perp a}, \; g_1^a, \; h_1^a, \;h_1^{\perp a},\; h_{1T}^{\perp a}$
and 2 leading--twist FFs $D_1^a, \; H_1^{\perp a}$ provide a basis
in the sense that in WW-type approximation all other TMDs and FFs 
can either be expressed in terms of these basis functions or vanish.
Below we shall see that, under the assumption of the validity of WW-type 
approximations, it is possible to express all SIDIS structure functions
in terms of the basis functions. \AP{Notice that SIDIS alone is of course not sufficient to determine
   the basis functions uniquely because the 8 basis functions appear
   in 6 SIDIS leading-twist structure functions. It is crucial to take advantage of
   other processes (such as Drell-Yan and hadron production in
   $e^+e^-$ annihilation, which are indispensable for the determination
   of $f_1^a$ and $D_1^a$).}
%\AP{Notice that SIDIS alone is of course not sufficient to determine the basis
%functions uniquely: the 8 basis functions appear in 6 \AP{leading-twist} SIDIS structure functions.
%It is crucial to take advantage of other processes: Drell--Yan for PDFs and TMDs
%and hadron production in $e^+e^-$ annihilation for FFs. Other processes 
%play also important roles.}
%Notice that SIDIS alone is of course not sufficient to determine the basis
%functions uniquely: \AP{8 twist-2 TMDs (or 6 ``basis'' TMDs) and 2 twist-2 TMD FFs appear in 15 structure functions (8 twist-2 and 5 sub-leading). 
%Definitely hadron production in $e^+e^-$ annihilation data is needed, each FF couples with 4 different twist-2 TMD PDFs, and so for each FF we have a case with 5 unknowns accessible in 4 twist-2 observables.
%It is crucial to take advantage of  Drell--Yan process for TMDs
%and other processes 
%play also important roles.}

These basis functions allow us to describe, in WW-type approximation,
all other TMDs. The experiment will tell us how well the approximations work.
In some cases, however, we know in advance that the WW-type approximations 
have limitations, see next Section~\ref{Sec-3.8:limitations}.
